\input{../common}

\title{Debian Games BoF}
\author[Evgeni Golov]{\href{mailto:evgeni@debian.org}{Evgeni Golov <evgeni@debian.org>}}
\institute{\href{http://www.debian.org/}{Debian/Ubuntu Games Team}}
\date[dc11]{26.07.2011, DebConf11}

\begin{document}

\frame{\titlepage}

\frame{
\frametitle{Who is the Games Team?}
\begin{itemize}
 \item actually "Debian/Ubuntu Games Team"
 \item 169 members\footnote{Alioth users}
 \item 277 packages in main
 \item 22 packages in contrib
 \item 12 packages in non-free
 \item<2-> pretty impressive, huh?
\end{itemize}
}

\frame{
\frametitle{Who is the Games Team?}
\begin{itemize}
 \item 74 inactive members\footnote{no mails and no svn/git commits since 01.01.2010}
 \item 539 bugs
 \item 4 of them grave
 \item 10 of them serious
 \item<2-> still impressive?
\end{itemize}
}

\frame{
\frametitle{What is being done?}
\begin{itemize}
 \item<1-> Monthly meetings (next one: August 7th, 12:00 UTC in
\#debian-games @ irc.debian.org)
 \item<2-> Policy is curently written (http://wiki.debian.org/Games/Policy)
 \item<3-> Interaction with other Distros is tried (but mostly fails)
\end{itemize}
}

\frame{
\frametitle{What has to be done?}
Disclaimer: \textbf{Evgeni}'s view, add yours at \\
\texttt{gobby-0.5 -c gobby.debian.net} $\rightarrow$ \texttt{dc11-games-bof}!
\begin{itemize}
 \item<2-> Clean up the Alioth group
 \begin{itemize}
  \item based on my own findings (\texttt{svn: pkg-games/software/list-inactive-members})
  \item also based on TeamMetrics? (Andreas Tille)
 \end{itemize}
 \item<3-> Do we need a homepage? Maybe as a Blends Tasks page? (Andreas Tille)
 \item<4-> Game Data Packager? Current commercial games? Humble Bundle?
 \item<5-> Backports?
 \item<6-> What do our users wish?
\end{itemize}
}
\section*{}

\frame{
  \frametitle{Join us!}
  \vfill
  \textcolor{debianblue}{\bf Debian/Ubuntu Games Team}\\[3mm]
  \texttt{debian-devel-games@lists.debian.org}\\[1em]
  \texttt{wiki.debian.org/Games}\\
  \texttt{\#debian-games @ irc.debian.org}\\
  \texttt{gobby-0.5 -c gobby.debian.net} $\rightarrow$ \texttt{dc11-games-bof}
}

\end{document}
